---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mycommonnames

<!-- badges: start -->
<!-- badges: end -->

An R package for exploring the most common first names in America using U.S. Social Security data.

## Overview
`mycommonnames` is an R package for exploring long-term trends in U.S. baby-name popularity (1880–2021).  
It provides a clean dataset (`names`), a Shiny app for interactive exploration, and a vignette that demonstrates name-trend analysis.


## Installation
You can install the development version from GitHub:

```r
# install.packages("devtools")
devtools::install_github("yourusername/mycommonnames")
```


## Example

How to load the data and run the app:

```r
library(mycommonnames)

# View the first few rows of the dataset
head(names)

# Launch the interactive app
launch_app()
```

## Launch the App

```{r, eval=FALSE}
mycommonnames::launch_app()
```


## Documentation
**Full site:** https://etc5523-2025.github.io/assignment-4-packages-and-shiny-apps-SumintraB/


